### 2017-09-01 paper/intro.tex
Moved content about flaky tests from intro to sec III
minor tweaks

At large organizations, the alternative of renting cloud
services\footnote{List of popular hosting cloud services:
  \url{https://clutch.co/cloud}} or even building proprietary
infrastructures for running tests is a legitimate approach to mitigate
the regression testing problem.  However, for projects with modest
 or nonexistent budgets and yet relatively heavy testing workloads, this solution may
not be economically viable.  For these cases, the use of commodity
hardware (\eg{}, existing workstations) is an attractive
solution for running tests.  The proliferation of
multi-core CPUs and the increasing popularization of testing
frameworks and build systems, which today provide mature support for
parallelization, enable\Comment{ test execution} speedups through increased CPU
usage~(see Section~\ref{sec:modes}).  These two elements~---~demand
for cost-effective test execution and supply of relatively inexpensive
testing infrastructures~---~led us to investigate the usage of
parallelism to speed up test execution.

@@

\vspace{1ex}\noindent\emph{Feasibility.}~To assess how prevalent
long-running test suites are we selected \numSubjs{} popular Java
projects from \github{} containing Maven build files~\cite{maven}.
Section~\ref{sec:eval} details our methodology to select subjects and
to isolate our experiments from environmental noise.  Results indicate
that nearly \percentMedLongRunning{} of the projects take at least 1m
to run their test suites and \percentLongRunning{} of the projects
take at least 5m to run their suites.  Considering the \numMedLong{}
projects in those two groups, the average execution time of a test
suite was \averageMedLongRunning{}.  Results also show that test cases
are typically short-running, typically taking less than half a second
to run.  Furthermore, we found that only in rare cases few test cases
monopolize execution cost associated with each test suite.

@@

\begin{itemize}
\item \emph{Incentivize forking.}~Forked JVMs manifest very low rates
  of test flakiness.  Developers of projects with long-running test
  suites should consider using that feature, which is available in
  modern build systems today (\eg{}, Maven).
\item \emph{Break test dependencies.}~Non-forked JVMs can achieve
  impressive speedups at the expense of sometimes impressive rates of
  flakiness.  Breaking test dependencies to avoid flakiness and take
  full advantage of those options is advised for developers with
  greater interest in efficiency.
\item \emph{Refactor tests for load balancing.}~Forked JVMs scales
  better with the number of cores when the test workload is balanced
  across testing classes.  To balance the workload, automated
  user-oblivious refactoring can help in scenarios where developers
  are not willing to change test code but have access to machines with
  a high number of cores.
\item \emph{Improve debugging for build systems.}~While preparing our
  experiments, we found scenarios\Comment{, related to test
    parallelization,} where Maven's executions did not reflect
  corresponding JUnit's executions. (Docker reproduction scripts
  available.) Those issues can hinder developers from using parallel
  testing. Better debugging infrastructure is important.
\end{itemize}

>>>>

At large organizations, the alternative of renting cloud
services~\cite{cloud-services} or even building proprietary
infrastructures for running tests is a legitimate approach to mitigate
the regression testing problem.  However, for projects with modest
 or nonexistent budgets and yet relatively heavy testing workloads, this solution may
not be economically viable.  For these cases, the use of commodity
hardware (\eg{}, existing workstations) is an attractive
solution for running tests.  The proliferation of
multi-core CPUs and the increasing popularization of testing
frameworks and build systems, which today provide mature support for
parallelization, enable\Comment{ test execution} speedups through increased CPU
usage~(see Section~\ref{sec:modes}).  These two elements~---~demand
for cost-effective test execution and supply of relatively inexpensive
testing infrastructures~---~led us to investigate the usage of
parallelism to speed up test execution.

@@

\vspace{1ex}\noindent\emph{Feasibility.}~To assess how prevalent
long-running test suites are we selected \numSubjs{} popular Java
projects from \github{} containing Maven build files~\cite{maven}.
Section~\ref{sec:eval} details our methodology to select subjects and
to isolate our experiments from environmental noise.  Results indicate
that nearly \percentMedLongRunning{} of the projects take at least 1m
to run and \percentLongRunning{} of the projects
take at least 5m to run.  Considering the \numMedLong{}
projects in those two groups, the average execution time of a test
suite was \averageMedLongRunning{}.  Results also show that test cases
are typically short-running, typically taking less than half a second
to run.  Furthermore, we found that only in rare cases few test cases
monopolize execution cost associated with each test suite.

@@

\setlist[itemize]{leftmargin=1.1em}
\begin{itemize}
\item \emph{Incentivize forking.}~Forked JVMs manifest very low rates
  of test flakiness.  Developers of projects with long-running test
  suites should consider using that feature, which is available in
  modern build systems today (\eg{}, Maven).
\item \emph{Break test dependencies.}~Non-forked JVMs can achieve
  impressive speedups at the expense of sometimes impressive rates of
  flakiness.  Breaking test dependencies to avoid flakiness and take
  full advantage of those options is advised for developers with
  greater interest in efficiency.
\item \emph{Refactor tests for load balancing.}~Forked JVMs scale
  better with the number of cores when the test workload is balanced
  across testing classes.  Automated refactoring could help balance
  the workload in scenarios where developers are not willing to change
  test code but have access to machines with a high number of cores.
\item \emph{Improve debugging for build systems.}~While preparing our
  experiments, we found scenarios\Comment{, related to test
    parallelization,} where Maven's executions did not reflect
  corresponding JUnit's executions. (Docker reproduction scripts
  available.) Those issues can hinder developers from using parallel
  testing. Better debugging infrastructure is important.
\end{itemize}
